Think deep for reef resilience

### 2025-07-11 paper/paper_draft.qmd
Adjust last paragraph
Ideally we'd think of moving these closer to the start

Incorporating the latest advancements in whole ecosystem larval connectivity modeling and
coral thermal response and adaptation research into coral population modeling allows an
investigation into how abiotic and biotic factors interact to influence coral climate change
resilience and the maintenance of positive carbonate budgets. Improvements in coral reef
climate response modeling, including sampling from a range of possible climate futures,
enable timeseries analyses of uncertain climate change and ecological scenarios [@bode2017;
@chollett2022; @donner2018; @klein2024; @uusitalo2015]. While it has previously been
suggested that highly connected source reefs that are resilient to bleaching and CoTS
outbreaks are likely to play a critical role in supporting future reef recovery across the
entire GBR [@hock2017], integrated modelling under current projections of Degree Heating
Weeks indicate that depth, rather than connectivity, plays a critical role in determining
reef resilience. It is further demonstrated that depth supports the maintenance of a postive
carbonate budget under all Global Climate Models.

>>>>

Incorporating the latest advancements in whole ecosystem larval connectivity modeling and
coral thermal response and adaptation research into coral population modeling allows an
investigation into how abiotic and biotic factors interact to influence coral climate change
resilience and the maintenance of positive carbonate budgets. Improvements in coral reef
climate response modeling, including sampling from a range of current projected climate
futures, enable timeseries analyses of uncertain climate change and ecological scenarios
[@bode2017; @chollett2022; @donner2018; @klein2024; @uusitalo2015].

It has previously been suggested that highly connected source reefs that are resilient to
bleaching and CoTS outbreaks are likely to play a critical role in supporting future reef
recovery across the entire GBR [@hock2017]. Integrated modelling incorporating data from the
latest advancements in coral population modelling [@ribeirodealmeida2024], whole of
ecosystem larval connectivity \[**citation**\], and current projections of Degree Heating
Weeks [@dixon2022; @dixon] indicate that depth, rather than connectivity, plays a more
critical role in reef resilience under projected conditions. It is further demonstrated that
deeper reefs support maintenance of positive carbonate budget under all climate projections.
